A generalized definition of multidimensional item response theory parameters

### 2022-11-18 output/paper_draft/paper_M2PLM_parameters.Rmd
Starts test space section (WIP) until definition of the inner product matrix elements.

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
Equation \@ref(eq:slope-param) makes it clear that a space $`r TEST_SPACE`$
with inner product matrix $`r INNER_PROD_MATRIX_INV`$ can be defined,
such that $`r INNER_PROD_DISCR_EQ`$ and, subsequently,
$`r DISCR_VECTOR_MODULE_EQ`$.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the
discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces,
as their inner product matrices are inverse of one another.

>>>>

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
Equation \@ref(eq:slope-param) makes it clear that a space $`r TEST_SPACE`$
with basis $`r ITEM_SPACE_BASIS_EQ`$ and inner product matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined,
such that $`r INNER_PROD_DISCR_EQ`$ and, subsequently,
$`r DISCR_VECTOR_MODULE_EQ`$.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the
discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces,
as their inner product matrices are inverse of one another.

With this definition we have that

\begin{equation}
  \begin{split}
    `r DIR_COS_ITEM_VEC_NORM_EQ` \\
    `r DISTANCE_PARAM_NORM_EQ`   \\
    `r SLOPE_MAX_PARAM_NORM_EQ`.
  \end{split}                             (\#eq:item-params-discrimination-norm)
\end{equation}
<!-- # TODO: Three equations collapsed into one altogether -->

It is clear that $`r INNER_PROD_INV_MAT_ELEMENT_EQ`$ were
$`r INNER_PROD_INV_MAT_ELEMENT`$ is the $`r INNER_PROD_INV_MAT_SUBINDEX`$-th
element of $`r INNER_PROD_MATRIX_INV`$.
<!-- # TODO: Error here? Mario means product of the basis elements? -->
